%----------------------------------------------------------------------------------------
%    DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------
\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%    PACKAGES & SETUP
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}     
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}        
\usepackage{multicol}
\usepackage{multirow}
\usepackage{fontawesome5}
\usepackage[unicode, draft=false]{hyperref}

% Centered column type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% Section formatting
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

% Link colors
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% Job header command for consistency
\newcommand{\jobheader}[3]{
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
        \textbf{#1} & \hfill & #2 \\
        \multicolumn{3}{@{}l@{}}{\small\textit{#3}} \\
    \end{tabularx}\vspace{-12pt}
}

% Itemized list environment
\newenvironment{jobitems}
    {
    \begin{itemize}[nosep, leftmargin=1.5em, itemsep=2pt, label=--]
    }
    {
    \end{itemize}
    }

%----------------------------------------------------------------------------------------
%    BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%    TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Nathan Cantafio} \\[7.5pt]
\href{https://nathancantafio.com/}{\faGlobe \ nathancantafio.com} \ $|$ \
\href{mailto:nathan.cantafio@stat.ubc.ca}{\faEnvelope \ nathan.cantafio@stat.ubc.ca} \ $|$ \ \href{https://github.com/nathan-cantafio}{\faGithub\ nathan-cantafio} \ $|$ \  
\href{https://www.linkedin.com/in/nathan-cantafio-0348203b3}{\faLinkedin\ nathan-cantafio}
\end{tabularx}

%----------------------------------------------------------------------------------------
%    EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{M.Sc. Statistics} & University of British Columbia & 2025--Present \\
\multicolumn{3}{@{}l@{}}{\small\textit{Cumulative Average: 94.5\% (A+ Letter Grade)}} \\ [3pt]

\textbf{B.Sc. Combined Honours, Mathematics and Statistics} & University of British Columbia & 2020--2025 \\
\multicolumn{3}{@{}l@{}}{\small\textit{Cumulative Average: 84\% (A- Letter Grade)}} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%    SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming} & Python (PyTorch, GPyTorch, NumPy), R (Tidyverse, ggplot2)\\
\textbf{Tools \& Software} & \LaTeX, Git, GitHub, Linux/Unix Shell (HPC), Weights and Biases, Microsoft Office \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%    EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\jobheader{Junior Statistical Consultant}{Mar 2026 -- Present}{Applied Statistics and Data Science Group (ASDA)}
\begin{jobitems}
    \item Collaborated with researchers across disciplines to provide experimental design advice and statistical analysis.
\end{jobitems}

\jobheader{First Generation Student Mentor}{Jan 2026 -- Apr 2026}{University of British Columbia}
\begin{jobitems}
    \item Provided academic guidance and professional development support to undergraduate students.
\end{jobitems}

\jobheader{Graduate Teaching Assistant}{Sep 2025 -- Jun 2026}{UBC Department of Statistics (STAT 305, STAT 302)}
\begin{jobitems}
    \item Held office hours, led weekly labs, and contributed to exam development across undergraduate courses.
\end{jobitems}

\jobheader{Undergraduate Summer Research Assistant}{May 2025 -- Aug 2025}{UBC Department of Statistics, supervised by Prof. Geoff Pleiss}
\begin{jobitems}
    \item Studied Gaussian processes and Bayesian Optimization using Python on Compute Canada HPC clusters.
\end{jobitems}

\jobheader{External Support Specialist Co-op}{Sep 2023 -- Aug 2024}{Chartered Professional Accountants of British Columbia}
\begin{jobitems}
    \item Provided technical support to stakeholders and authored an internal troubleshooting wiki.
\end{jobitems}

%----------------------------------------------------------------------------------------
%    PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\jobheader{Pok\'emon Team Building Optimization}{\href{https://github.com/nathan-cantafio/pokemon}{Link to Repo}}{STAT 535C Class Project}
\begin{jobitems}
    \item Applied black-box optimization techniques to discover strong Pok\'emon teams.
\end{jobitems}

\jobheader{Pandemic Simulation Experiment}{\href{https://github.com/nathan-cantafio/pandemic-simulation}{Link to Repo}}{STAT 404 Class Project}
\begin{jobitems}
    \item Designed a simulation experiment to assess policy effectiveness in preventing disease spread.
\end{jobitems}

\jobheader{Mortgage vs. Rent Simulation}{\href{https://github.com/nathan-cantafio/mortgages}{Link to Repo}}{Personal Project}
\begin{jobitems}
    \item Estimated long-term housing costs using Monte Carlo simulations and Vasicek/CIR interest rate models.
\end{jobitems}

%----------------------------------------------------------------------------------------
%    AWARDS
%----------------------------------------------------------------------------------------
\section{Awards}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{Constance van Eeden Scholar Award} & University of British Columbia & 2025 \\
\textbf{NSERC Undergraduate Student Research Award (USRA)} & University of British Columbia & 2025 \\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}